---
title: "BST 260_Happy Highs"
author: "Seranne Motital, Shravanthi Seshasayee, Sanjana Sunderesan"
date: "9 December 2017"
output: html_document
---

```{r echo=FALSE}
library(dplyr)
library(tidyverse)
library(knitr)
```

# Overview and Motivation
The World Happiness Report is a composite measure of country-level happiness based on economic and social factors such as per capita GDP, social support, healthy life expectancy at birth, freedom to make life choices, generosity and perceptions of corruption, released annually by the UN Sustainble Development Solutions Network. In the present landscape of shifting political and economic climates across the world, we believe it is important to expand and include measures which encompass a wider narrative of the human experience. We are keen to understand the association between country-level physical, financial, social, cultural, political, and environmental indicators and the parent country's ranking on an overall well-being index. For instance, tt would be interesting to learn more about the influences of variables such as Gini Coefficients, literacy levels, deforestation, climate etc. on the happiness ranking of a country. 

We hope to understand the underlying variables most responsible for these scores, and identify conceptual and measurement gaps in the development of an overall score of country-level well-being. We believe that factors such as racial diversity, environmental sustainability, and population skew, among others, are either missing or underrepresented in the present composite measure. We aim to modify this to build a more well-rounded measure of the well-being of a country.  
We believe that this information could potentially inform policies to improve overall country happiness and human flourishing.  

# Related Work:  Anything that inspired you, such as a paper, a web site, or something we discussed in class.

# Initial Questions: What questions are you trying to answer? How did these questions evolve over the course of the project? What new questions did you consider in the course of your analysis?

We began our project with the goal of identifying yearly-changes in a country's happiness and well-being. However, as we learnt more about how these composite indices are derived, we grew keen to understand the factors considered in the creation of a well-being score. Over the course of our literature review, we identified more variables we believe are relevant to a population's well-being, and decided to create a new, incremented ranking of country well-being with this additional data. Thus, our project seeks to answer: 

- Is there a change in the average ranking of a country's happiness and well-being, given the inclusion of a more comprehensive variable list representing its physical, social, cultural, economic and political enviroments?
- Are are specific variables which contribute more to this derived composite index, than others?


# Data: Source, scraping method, cleanup, etc.

In order to develop our well-being index, we extracted data from a number of resources, categorized below: (To make a table displaying our variables with categories). 
```{r}
cnames <- c("Category", "Indicator Variable", "Data Source")

categs <- c("Population Charateristics", "Child Welfare", "Gender", "Employment","Economic Indicators", "Energy Indicators", "Emissions", "Connectivity", "Environmental Welfare", "Food Deficit", "Sense of Security", "Travel for Leisure"  )

#dsources <- c("World Bank: World Development Indicators", "Happy Planet Index", "Wikipedia", "UN SDSN: World Happiness Report")

dframe1 %>% data.frame("Indicators" = categs) %>% kable

```

From each of our sources, we selected variables most relevant to the creation of our composite index (based on literature review). A Pearson's correlation was run across all chosen variables, to identify 


and generated a country-wise ranking for each variable, in every category. Every category then received its own composite scoring  

# Exploratory Analysis: What visualizations did you use to look at your data in different ways? What are the different statistical methods you considered? Justify the decisions you made, and show any major changes to your ideas. How did you reach these conclusions?

- Scatterplot of the WHR countries ranks?
- Association between maybe ethnic fractionalization/total population/environmental biodiversity and these ranks? [T perhaps justify why we don't think that these ranks are very accurate]

```{r}

```

## Methods: 

# Deriving data from the World Development Indicators

```{r}

```{r}
library(readr)
library(tidyverse)
```

```{r}
Indicators_csv <- read_csv("d:/Documents/IntroDSproject/Indicators_csv")
# Filtering by Year
WDI <- filter(Indicators_csv, Year == "2010"| Year == "2011" | Year == "2012"| Year == "2013" | Year == "2014" | Year == "2015" | Year == "2016" | Year =="2017")
```

```{r}
#ourWDI <- read_csv("F://IntroDSproject/ourWDI.csv")

# Removing Aggregated country values              

WDInew <- filter(WDI, CountryCode != "WBG")
WDInew <- filter(WDInew, CountryCode != "WLD")
WDInew <- filter(WDInew, CountryCode != "UMC")
WDInew <- filter(WDInew, CountryCode != "SSA")
WDInew <- filter(WDInew, CountryCode != "SSF")
WDInew <- filter(WDInew, CountryCode != "OED")
WDInew <- filter(WDInew, CountryCode != "MNA")
WDInew <- filter(WDInew, CountryCode != "MEA")
WDInew <- filter(WDInew, CountryCode != "LMC")
WDInew <- filter(WDInew, CountryCode != "LIC")
WDInew <- filter(WDInew, CountryCode != "LMY")
WDInew <- filter(WDInew, CountryCode != "LDC")
WDInew <- filter(WDInew, CountryCode != "LAC")
WDInew <- filter(WDInew, CountryCode != "LCN")
WDInew <- filter(WDInew, CountryCode != "OEC")
WDInew <- filter(WDInew, CountryCode != "NOC")
WDInew <- filter(WDInew, CountryCode != "HIC")
WDInew <- filter(WDInew, CountryCode != "HPC")
WDInew <- filter(WDInew, CountryCode != "FCS")
WDInew <- filter(WDInew, CountryCode != "EUU")
WDInew <- filter(WDInew, CountryCode != "ECA")
WDInew <- filter(WDInew, CountryCode != "ECS")
WDInew <- filter(WDInew, CountryCode != "EMU")
WDInew <- filter(WDInew, CountryCode != "EAP")
WDInew <- filter(WDInew, CountryCode != "EAS")
WDInew <- filter(WDInew, CountryCode != "CEB")
WDInew <- filter(WDInew, CountryCode != "ARB")
WDInew <- filter(WDInew, CountryCode != "NAC")
WDInew <- filter(WDInew, CountryCode != "SAS")
WDInew <- filter(WDInew, CountryCode != "MIC")


WDI2 <- filter(WDInew, IndicatorCode == "AG.LND.FRST.ZS" | IndicatorCode == "EG.FEC.RNEW.ZS"|IndicatorCode == "EG.USE.COMM.FO.ZS"|IndicatorCode == "EG.ELC.ACCS.ZS"|IndicatorCode == "EG.USE.ELEC.KH.PC"| IndicatorCode == "EN.ATM.CO2E.PC"|IndicatorCode == "ER.PTD.TOTL.ZS"| IndicatorCode == "EN.POP.DNST"|IndicatorCode == "ER.PTD.TOTL.ZS"|IndicatorCode == "FP.CPI.TOTL.ZG"|IndicatorCode == "GC.XPN.COMP.ZS"|IndicatorCode == "IC.FRM.CRIM.ZS"|IndicatorCode == "IC.FRM.FEMM.ZS"|IndicatorCode == "IC.LGL.CRED.XQ"|IndicatorCode == "IT.CEL.SETS.P2"|IndicatorCode == "IT.NET.USER.P2"|IndicatorCode == "MS.MIL.XPND.GD.ZS"|IndicatorCode == "NY.GDP.PCAP.CD"|IndicatorCode == "NY.GDP.MKTP.PP.CD"|IndicatorCode == "NY.GDP.PCAP.KD.ZG"|IndicatorCode == "SE.ADT.1524.LT.ZS"|IndicatorCode == "SE.ADT.LITR.ZS"|IndicatorCode == "SG.GEN.PARL.ZS"|IndicatorCode == "SG.VAW.REAS.ZS"|IndicatorCode == "SH.DTH.MORT"|IndicatorCode == "SI.POV.GINI"|IndicatorCode == "SL.EMP.WORK.ZS"|IndicatorCode == "SL.FAM.0714.ZS"|IndicatorCode == "SP.DYN.IMRT.IN"|IndicatorCode == "SL.UEM.NEET.ZS"|IndicatorCode == "SM.POP.TOTL.ZS"|IndicatorCode == "SN.ITK.DFCT"|IndicatorCode == "SP.DYN.LE00.IN"|IndicatorCode == "SP.UWT.TFRT"|IndicatorCode == "ST.INT.DPRT"|IndicatorCode == "SP.POP.TOTL"|IndicatorCode == "VC.IHR.PSRC.P5")


write.csv(WDI2, file = "ourWDI.csv")
WDI4<- select(WDI2,"CountryName","CountryCode", "IndicatorCode", "Year","Value")

energy <- WDI4%>% filter(IndicatorCode == "EG.FEC.RNEW.ZS"|IndicatorCode == "EG.USE.COMM.FO.ZS"|IndicatorCode == "EG.ELC.ACCS.ZS"|IndicatorCode == "EG.USE.ELEC.KH.PC") %>% spread(IndicatorCode, Value)
write.csv(energy, file = "Energy.csv")


emissions <- WDI4%>% filter(IndicatorCode == "EN.ATM.CO2E.PC")%>% spread(IndicatorCode, Value)
write.csv(emissions, file = "Emissions.csv")


environnment1 <- WDI4 %>% filter(IndicatorCode == "ER.PTD.TOTL.ZS"|IndicatorCode == "AG.LND.FRST.ZS") %>% spread(IndicatorCode, Value)
write.csv(environnment1, file = "Environment.csv")


Security <- WDI4 %>% filter(IndicatorCode == "VC.IHR.PSRC.P5"|IndicatorCode == "IC.LGL.CRED.XQ") %>% spread(IndicatorCode, Value)
write.csv(Security, file = "Security.csv")

comm <- WDI4 %>% filter(IndicatorCode == "IT.CEL.SETS.P2"|IndicatorCode == "IT.NET.USER.P2")  %>% spread(IndicatorCode, Value)
write.csv(comm, file = "Communication.csv")


GDP <- WDI4 %>% filter(IndicatorCode == "MS.MIL.XPND.GD.ZS"|IndicatorCode == "NY.GDP.PCAP.CD"|IndicatorCode == "NY.GDP.MKTP.PP.CD"|IndicatorCode == "NY.GDP.PCAP.KD.ZG"|IndicatorCode == "FP.CPI.TOTL.ZG") %>% spread(IndicatorCode, Value)
write.csv(GDP, file = "GDP.csv")

Education <- WDI4 %>% filter(IndicatorCode == "SE.ADT.1524.LT.ZS"|IndicatorCode == "SE.ADT.LITR.ZS") %>% spread(IndicatorCode, Value)
write.csv(Education, file = "Education.csv")

Gender <- WDI4 %>% filter(IndicatorCode == "SG.GEN.PARL.ZS"|IndicatorCode == "SP.UWT.TFRT") %>% spread(IndicatorCode, Value)
write.csv(Gender, file = "Gender.csv")


Population <- WDI4 %>% filter(IndicatorCode == "SI.POV.GINI"|IndicatorCode == "SM.POP.TOTL.ZS"|IndicatorCode == "SP.DYN.LE00.IN" | IndicatorCode == "SP.POP.TOTL"| IndicatorCode == "EN.POP.DNST") %>% spread(IndicatorCode, Value)
write.csv(Population, file = "Population.csv")

Employment<- WDI4 %>% filter(IndicatorCode == "SL.EMP.WORK.ZS") %>% spread(IndicatorCode, Value)
write.csv(Employment, file = "Employment.csv")

Children<- WDI4 %>% filter(IndicatorCode == "SL.FAM.0714.ZS"|IndicatorCode == "SL.UEM.NEET.ZS" | IndicatorCode == "SP.DYN.IMRT.IN") %>% spread(IndicatorCode, Value)
write.csv(Children, file = "Children.csv")

FoodDeficit <- WDI4 %>% filter(IndicatorCode == "SN.ITK.DFCT") %>% spread(IndicatorCode, Value)
write.csv(FoodDeficit, file = "Food_deficit.csv")

Tourism <- WDI4 %>% filter(IndicatorCode == "ST.INT.DPRT") %>% spread(IndicatorCode, Value)
write.csv(Tourism, file = "Tourism.csv")
```

#Deriving Data from the World Happiness Report Dataset

# Deriving Data from the Happy Panet Index

# Checking for correlations between indicators chosen based on literature review

# Deriving category-level scores 

# Deriving new well-rounded well-being index 



## Final Analysis: What did you learn about the data? How did you answer the questions? How can you justify your answers?
