---
title: "Plots and Interactives"
author: "Seranne Motital, Shravanthi Seshasayee, Sanjana Sunderesan"
date: "9 December 2017"
output: html_document
---
```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(maps)
library(ggmap)
library(rworldmap)



```

```{r}
# To change individual NAs to a particular value 
#which(is.na(CalculatedOurindex), arr.ind=TRUE)
#data.frame[row_number, column_number] = new_value
```

Plots/Models we could make:

1. EDA:

- Existing WHR scores by country 

```{r}
gh15 <- read_csv("/IntroDSproject/Source Data/World Happiness Report/2015.csv")
colnames(gh15)[1] <-"country"
colnames(gh15)[3] <- "happiness.rank"
View(gh15)
gh16 <- read_csv("/IntroDSproject/Source Data/World Happiness Report/2016.csv")
colnames(gh16)[1] <-"country"
colnames(gh16)[3] <- "happiness.rank"
gh17 <- read_csv("/IntroDSproject/Source Data/World Happiness Report/2017.csv")
colnames(gh17)[1] <-"country"
colnames(gh17)[2] <- "happiness.rank"


plot1 <- ggplot(gh15, aes(country, happiness.rank, col = Region)) + geom_point() + geom_map(map_id = )
plot1

worldMapEnv

worldMap <- borders("world", colour="gray50", fill="gray50")

ggplot(gh15, aes(map_id = gh15$Region)) + 
    geom_map(aes(fill = value), map = worldMap, color='grey', size=0.3) + 
    expand_limits(x = worldMap$long, y = worldMap$lat) +
    theme_few()+
    theme(legend.position = "bottom",
         axis.ticks = element_blank(), 
         axis.title = element_blank(), 
         axis.text =  element_blank()) +
    scale_fill_gradient(low="white", high="darkblue", name="Number of Affiliates") +
    guides(fill = guide_colorbar(barwidth = 10, barheight = .5))




#Now Layer the cities on top
mp <- mp+ geom_point(gh15, aes(country, region) ,col = gh15$happiness.rank, size=3) 
mp


```


- Existing HPI scores by counrty 
- Difference between EF indices distribution and existing WHR (this is what they didn't consider!)
- Sample Category Rankings 

2. Results

- Sample category rankings 
- Our Index rankings by country 
- 


3. Predictions/Interactives
- Shiny app for a country in our index where you could change value of something, and its rank moves?




```{r}

```

