---
title: "Plots and Interactives"
author: "Seranne Motital, Shravanthi Seshasayee, Sanjana Sunderesan"
date: "9 December 2017"
output: html_document
---
```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(maps)
library(ggmap)
library(rworldmap)
```

```{r}
# To change individual NAs to a particular value 
#which(is.na(CalculatedOurindex), arr.ind=TRUE)
#data.frame[row_number, column_number] = new_value
```
Plots/Models we could make:

1. EDA:

- Existing WHR scores by Region 

```{r, echo=TRUE}
whr <- read_csv("/IntroDSproject/Source Data/World Happiness Report/2016.csv")
our <- read_csv("/IntroDSproject/Final score data/CalculatedOurindex.csv")
View(whr)
colnames(whr)[3] <- "happiness.rank"
colnames(whr)[7] <- "gdp"


x <- whr %>% filter(!is.na(gdp)) %>% select("gdp")
x<- x$gdp
max(x)
x <- cut(as.numeric(x), c(0, 0.1005, 1.2236, 1.82427))
x = factor(x, labels = c("Low-Income Countries", "Middle Income Countres", "High-Income Countries"))

whr %>% ggplot(aes(x = Region, y = -happiness.rank, col = x)) + geom_point() + geom_jitter(width = 0, height = 0.5) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + scale_colour_manual(breaks = c("Low-Income Countries", "Middle Income Countres", "High-Income Countries"), values = c("red", "blue", "green")) + ylab("2016 World Happiness Report Ranking") + xlab("Countries by Region") + ggtitle("2016 World Happiness Report Ranking")

```

```{r, EVAL = FALSE}
x <- read.csv("/IntroDSproject/Final score data/CalculatedOurindex.csv")

#x <- cut(as.numeric(x), c(0, 0.1005, 1.2236, 1.82427))

x <- x %>% group_by(sub.region) %>% mutate(meanrank = round(mean(finalindex, na.rm = TRUE)))

x %>% ggplot(aes(sub.region, meanrank)) + geom_point() + theme(axis.text.x = element_text(angle = 90, hjust = 1)) +geom_bar()
```



- Existing HPI scores by Region





- Difference between EF indices distribution and existing WHR (this is what they didn't consider!)
- Sample Category Rankings 

2. Results

- Sample category rankings 
- Our Index rankings by country 
- Our variables regressed against a negative outcome


3. Predictions/Interactives
- Shiny app for a country in our index where you could change value of something, and its rank moves?


```{r}

```

```{r}
gh15 <- read_csv("/IntroDSproject/Source Data/World Happiness Report/2015.csv")
colnames(gh15)[1] <-"country"
colnames(gh15)[3] <- "happiness.rank"
View(gh15)
gh16 <- read_csv("/IntroDSproject/Source Data/World Happiness Report/2016.csv")
colnames(gh16)[1] <-"country"
colnames(gh16)[3] <- "happiness.rank"
gh17 <- read_csv("/IntroDSproject/Source Data/World Happiness Report/2017.csv")
colnames(gh17)[1] <-"country"
colnames(gh17)[2] <- "happiness.rank"


rankfac <- as.factor(gh15$happiness.rank)
map.world <- map_data("world")
map.world_joined <- left_join(map.world, gh15, by = c('region' = 'country'))
#map.world_joined <- map.world_joined %>% mutate(fill_flg = ifelse(is.na(happiness.rank),F,T))
head(map.world_joined)

ggplot() +
  geom_polygon(data = map.world_joined, aes(x = long, y = lat, group = group, fill = rankfac)) +
    scale_fill_manual(values = c("#CCCCCC","#e60000")) +
  labs(title = 'Test"'
       ,subtitle = "Testing still ")

```



```