<<<<<<< HEAD
---
title: "WDI"
output: html_document
---

```{r}
library(readr)
library(tidyverse)
```

```{r}
Indicators_csv <- read_csv("d:/Documents/IntroDSproject/Indicators_csv")
# Filtering by Year
WDI <- filter(Indicators_csv, Year == "2010"| Year == "2011" | Year == "2012"| Year == "2013" | Year == "2014" | Year == "2015" | Year == "2016" | Year =="2017")
```

```{r}
ourWDI <- read_csv("F://IntroDSproject/ourWDI.csv")

# Removing Aggregated country values              

WDInew <- filter(ourWDI, CountryCode != "WBG")
WDInew <- filter(WDInew, CountryCode != "WLD")
WDInew <- filter(WDInew, CountryCode != "UMC")
WDInew <- filter(WDInew, CountryCode != "SSA")
WDInew <- filter(WDInew, CountryCode != "SSF")
WDInew <- filter(WDInew, CountryCode != "OED")
WDInew <- filter(WDInew, CountryCode != "MNA")
WDInew <- filter(WDInew, CountryCode != "MEA")
WDInew <- filter(WDInew, CountryCode != "LMC")
WDInew <- filter(WDInew, CountryCode != "LIC")
WDInew <- filter(WDInew, CountryCode != "LMY")
WDInew <- filter(WDInew, CountryCode != "LDC")
WDInew <- filter(WDInew, CountryCode != "LAC")
WDInew <- filter(WDInew, CountryCode != "LCN")
WDInew <- filter(WDInew, CountryCode != "OEC")
WDInew <- filter(WDInew, CountryCode != "NOC")
WDInew <- filter(WDInew, CountryCode != "HIC")
WDInew <- filter(WDInew, CountryCode != "HPC")
WDInew <- filter(WDInew, CountryCode != "FCS")
WDInew <- filter(WDInew, CountryCode != "EUU")
WDInew <- filter(WDInew, CountryCode != "ECA")
WDInew <- filter(WDInew, CountryCode != "ECS")
WDInew <- filter(WDInew, CountryCode != "EMU")
WDInew <- filter(WDInew, CountryCode != "EAP")
WDInew <- filter(WDInew, CountryCode != "EAS")
WDInew <- filter(WDInew, CountryCode != "CEB")
WDInew <- filter(WDInew, CountryCode != "ARB")
WDInew <- filter(WDInew, CountryCode != "NAC")


WDI2 <- filter(WDInew, IndicatorCode == "AG.LND.FRST.ZS" | IndicatorCode == "EG.FEC.RNEW.ZS"|IndicatorCode == "EG.USE.COMM.FO.ZS"|IndicatorCode == "EG.ELC.ACCS.ZS"| IndicatorCode == "EN.ATM.CO2E.PC"| IndicatorCode == "EN.ATM.GHGO.KT.CE"|IndicatorCode == "EN.ATM.METH.KT.CE"|IndicatorCode == "ER.PTD.TOTL.ZS"| IndicatorCode == "EN.POP.DNST"|IndicatorCode == "ER.PTD.TOTL.ZS"|IndicatorCode == "FP.CPI.TOTL.ZG"|IndicatorCode == "GC.XPN.COMP.ZS"|IndicatorCode == "IC.FRM.CRIM.ZS"|IndicatorCode == "IC.FRM.FEMM.ZS"|IndicatorCode == "IC.LGL.CRED.XQ"|IndicatorCode == "IT.CEL.SETS.P2"|IndicatorCode == "IT.NET.USER.P2"|IndicatorCode == "MS.MIL.XPND.GD.ZS"|IndicatorCode == "NY.GDP.PCAP.CD"|IndicatorCode == "NY.GDP.MKTP.PP.CD"|IndicatorCode == "NY.GDP.PCAP.KD.ZG"|IndicatorCode == "SE.ADT.1524.LT.ZS"|IndicatorCode == "SE.ADT.LITR.ZS"|IndicatorCode == "SG.GEN.PARL.ZS"|IndicatorCode == "SG.VAW.REAS.ZS"|IndicatorCode == "SH.DTH.MORT"|IndicatorCode == "SI.POV.GINI"|IndicatorCode == "SL.EMP.WORK.ZS"|IndicatorCode == "SL.FAM.0714.ZS"|IndicatorCode == "SL.UEM.NEET.ZS"|IndicatorCode == "SM.POP.TOTL.ZS"|IndicatorCode == "SN.ITK.DFCT"|IndicatorCode == "SP.DYN.LE00.IN"|IndicatorCode == "SP.UWT.TFRT"|IndicatorCode == "ST.INT.DPRT"|IndicatorCode == "SP.POP.TOTL"|IndicatorCode == "VC.IHR.PSRC.P5")
=======
read.csv("F://IntroDSproject/ourWDI.csv")

# Removing Aggregated country values              

WDI <- filter(ourWDI, CountryCode != "WBG" | CountryCode != "WLD" | CountryCode != "UMC" | CountryCode != "SSA" | CountryCode != "SSF" | CountryCode != "OED" | CountryCode != "MNA" | CountryCode != "MEA" | CountryCode != "LMC" | CountryCode != "LIC" | CountryCode != "LMY" | CountryCode != "LDC" | CountryCode != "LAC" | CountryCode != "LCN" | CountryCode != "OEC" | CountryCode != "NOC" | CountryCode != "HIC" | CountryCode != "HPC" | CountryCode != "FCS" | CountryCode != "EUU" | CountryCode != "ECA" | CountryCode != "ECS" | CountryCode != "EMU" | CountryCode != "EAP" | CountryCode != "EAS" | CountryCode != "CEB" | CountryCode != "ARB")


WDI2 <- filter(WDI, IndicatorCode == "AG.LND.FRST.ZS" | IndicatorCode == "EG.FEC.RNEW.ZS"|IndicatorCode == "EG.USE.COMM.FO.ZS"|IndicatorCode == "EG.ELC.ACCS.ZS"| IndicatorCode == "EN.ATM.CO2E.PC"| IndicatorCode == "EN.ATM.GHGO.KT.CE"|IndicatorCode == "EN.ATM.METH.KT.CE"|IndicatorCode == "ER.PTD.TOTL.ZS"| IndicatorCode == "EN.POP.DNST"|IndicatorCode == "ER.PTD.TOTL.ZS"|IndicatorCode == "FP.CPI.TOTL.ZG"|IndicatorCode == "GC.XPN.COMP.ZS"|IndicatorCode == "IC.FRM.CRIM.ZS"|IndicatorCode == "IC.FRM.FEMM.ZS"|IndicatorCode == "IC.LGL.CRED.XQ"|IndicatorCode == "IT.CEL.SETS.P2"|IndicatorCode == "IT.NET.USER.P2"|IndicatorCode == "MS.MIL.XPND.GD.ZS"|IndicatorCode == "NY.GDP.PCAP.CD"|IndicatorCode == "NY.GDP.MKTP.PP.CD"|IndicatorCode == "NY.GDP.PCAP.KD.ZG"|IndicatorCode == "SE.ADT.1524.LT.ZS"|IndicatorCode == "SE.ADT.LITR.ZS"|IndicatorCode == "SG.GEN.PARL.ZS"|IndicatorCode == "SG.VAW.REAS.ZS"|IndicatorCode == "SH.DTH.MORT"|IndicatorCode == "SI.POV.GINI"|IndicatorCode == "SL.EMP.WORK.ZS"|IndicatorCode == "SL.FAM.0714.ZS"|IndicatorCode == "SL.UEM.NEET.ZS"|IndicatorCode == "SM.POP.TOTL.ZS"|IndicatorCode == "SN.ITK.DFCT"|IndicatorCode == "SP.DYN.LE00.IN"|IndicatorCode == "SP.UWT.TFRT"|IndicatorCode == "ST.INT.DPRT"|IndicatorCode == "SP.POP.TOTL"|IndicatorCode == "VC.IHR.PSRC.P5")

write.csv(WDI2, file = "ourWDI.csv")
WDI4<- select(WDI2,"CountryName","CountryCode", "IndicatorCode", "Year","Value")

energy<- WDI4%>% filter(IndicatorCode == "EG.FEC.RNEW.ZS"|IndicatorCode == "EG.USE.COMM.FO.ZS"|IndicatorCode == "EG.ELC.ACCS.ZS") %>% spread(IndicatorCode, Value)
write.csv(energy, file = "Energy.csv")


emissions<- WDI4%>% filter(IndicatorCode == "EN.ATM.CO2E.PC"| IndicatorCode == "EN.ATM.GHGO.KT.CE"|IndicatorCode == "EN.ATM.METH.KT.CE")%>% spread(IndicatorCode, Value)
write.csv(emissions, file = "Emissions.csv")


environnment1<- WDI4 %>% filter(IndicatorCode == "ER.PTD.TOTL.ZS"|IndicatorCode == "AG.LND.FRST.ZS") %>% spread(IndicatorCode, Value)
write.csv(environnment1, file = "Environment.csv")


econ<- WDI4 %>% filter(IndicatorCode == "FP.CPI.TOTL.ZG"|IndicatorCode == "IC.FRM.CRIM.ZS"|IndicatorCode == "IC.LGL.CRED.XQ") %>% spread(IndicatorCode, Value)
write.csv(econ, file = "Economy.csv")


comm<- WDI4 %>% filter(IndicatorCode == "IT.CEL.SETS.P2"|IndicatorCode == "IT.NET.USER.P2")  %>% spread(IndicatorCode, Value)
write.csv(comm, file = "Communication.csv")


GDP<- WDI4 %>% filter(IndicatorCode == "MS.MIL.XPND.GD.ZS"|IndicatorCode == "NY.GDP.PCAP.CD"|IndicatorCode == "NY.GDP.MKTP.PP.CD"|IndicatorCode == "NY.GDP.PCAP.KD.ZG") %>% spread(IndicatorCode, Value)
write.csv(GDP, file = "GDP.csv")

population<- WDI4 %>% filter(IndicatorCode == "SH.DTH.MORT"|IndicatorCode == "SI.POV.GINI"|IndicatorCode == "SL.EMP.WORK.ZS"|IndicatorCode == "SL.FAM.0714.ZS"|IndicatorCode == "SL.UEM.NEET.ZS"|IndicatorCode == "SM.POP.TOTL.ZS"|IndicatorCode == "SN.ITK.DFCT"|IndicatorCode == "SP.DYN.LE00.IN"|IndicatorCode == "SP.UWT.TFRT"|IndicatorCode == "ST.INT.DPRT"|IndicatorCode == "SP.POP.TOTL"|IndicatorCode == "VC.IHR.PSRC.P5"| IndicatorCode == "EN.POP.DNST") %>% spread(IndicatorCode, Value)

write.csv(population, file = "Population.csv")

```
(AG.LND.FRST.ZS	Forest area (% of land area), 
EG.ELC.ACCS.ZS	Access to electricity (% of population) 
EG.FEC.RNEW.ZS	Renewable energy consumption (% of total final energy consumption), 
EG.USE.COMM.FO.ZS	Fossil fuel energy consumption (% of total), 
EN.ATM.CO2E.PC	CO2 emissions (metric tons per capita), 
EN.ATM.GHGO.KT.CE	Other greenhouse gas emissions, HFC, PFC and SF6 (thousand metric tons of CO2 equivalent), 
EN.ATM.HFCG.KT.CE	HFC gas emissions (thousand metric tons of CO2 equivalent, 
EN.ATM.METH.KT.CE	Methane emissions (kt of CO2 equivalent), 
EN.FSH.THRD.NO	Fish species, threatened, 
EN.HPT.THRD.NO	Plant species (higher), threatened, 
EN.MAM.THRD.NO	Mammal species, threatened, 
EN.POP.DNST	Population density (people per sq. km of land area), 
ER.BDV.TOTL.XQ	GEF benefits index for biodiversity (0 = no biodiversity potential to 100 = maximum), 
ER.PTD.TOTL.ZS	Terrestrial and marine protected areas (% of total territorial area), 
FP.CPI.TOTL.ZG	Inflation, consumer prices (annual %), 
GC.XPN.COMP.ZS	Compensation of employees (% of expense), 
IC.FRM.CRIM.ZS	Losses due to theft, robbery, vandalism, and arson (% sales), 
IC.FRM.FEMM.ZS	Firms with female top manager (% of firms),
IC.LGL.CRED.XQ	Strength of legal rights index (0=weak to 12=strong),
IT.CEL.SETS.P2	Mobile cellular subscriptions (per 100 people), 
IT.NET.USER.P2	Internet users (per 100 people), 
MS.MIL.XPND.GD.ZS	Military expenditure (% of GDP), 
NY.GDP.PCAP.CD	GDP per capita (current USdollar), NY.GDP.MKTP.PP.CD	GDP, PPP (current international dollar), 
NY.GDP.PCAP.KD.ZG	GDP per capita growth (annual %), 
SE.ADT.1524.LT.ZS	Youth literacy rate, population 15-24 years, both sexes (%), 
SE.ADT.LITR.ZS	Adult literacy rate, population 15+ years, both sexes (%), 
SG.GEN.PARL.ZS	Proportion of seats held by women in national parliaments (%), 
SG.VAW.REAS.ZS	Women who believe a husband is justified in beating his wife (any of five reasons) (%),
SH.DTH.MORT	Number of under-five deaths), 
SI.POV.GINI	GINI index (World Bank estimate), 
SL.EMP.WORK.ZS	Wage and salaried workers, total (% of total employed), 
SL.FAM.0714.ZS	Children in employment, unpaid family workers (% of children in employment, ages 7-14),
SL.UEM.NEET.ZS	Share of youth not in education, employment, or training, total (% of youth population, SM.POP.TOTL.ZS	International migrant stock (% of population),
SN.ITK.DFCT	Depth of the food deficit (kilocalories per person per day), 
SP.DYN.LE00.IN	Life expectancy at birth, total (years), 
SP.UWT.TFRT	Unmet need for contraception (% of married women ages 15-49), 
ST.INT.DPRT	International tourism, number of departures, 
SP.POP.TOTL	Population, total, 
VC.IHR.PSRC.P5	Intentional homicides (per 100,000 people))

```{r}
ourWDI <- read_csv("d:/Documents/GitHub/IntroDSproject/ourWDI.csv")
head(ourWDI)


```


#https://www.kaggle.com/benhamner/indicators-in-data
=======
---
title: "WDI"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(readr)
Indicators_csv <- read_csv("d:/Documents/IntroDSproject/Indicators_csv")
library(tidyverse)

# Filtering by Year
WDI <- filter(Indicators_csv, Year == "2010"| Year == "2011" | Year == "2012"| Year == "2013" | Year == "2014" | Year == "2015" | Year == "2016" | Year =="2017")

ourWDI <- read.csv("F://IntroDSproject/ourWDI.csv")

# Removing Aggregated country values              

WDInew <- filter(ourWDI, CountryCode != "WBG")
WDInew <- filter(WDInew, CountryCode != "WLD")
WDInew <- filter(WDInew, CountryCode != "UMC")
WDInew <- filter(WDInew, CountryCode != "SSA")
WDInew <- filter(WDInew, CountryCode != "SSF")
WDInew <- filter(WDInew, CountryCode != "OED")
WDInew <- filter(WDInew, CountryCode != "MNA")
WDInew <- filter(WDInew, CountryCode != "MEA")
WDInew <- filter(WDInew, CountryCode != "LMC")
WDInew <- filter(WDInew, CountryCode != "LIC")
WDInew <- filter(WDInew, CountryCode != "LMY")
WDInew <- filter(WDInew, CountryCode != "LDC")
WDInew <- filter(WDInew, CountryCode != "LAC")
WDInew <- filter(WDInew, CountryCode != "LCN")
WDInew <- filter(WDInew, CountryCode != "OEC")
WDInew <- filter(WDInew, CountryCode != "NOC")
WDInew <- filter(WDInew, CountryCode != "HIC")
WDInew <- filter(WDInew, CountryCode != "HPC")
WDInew <- filter(WDInew, CountryCode != "FCS")
WDInew <- filter(WDInew, CountryCode != "EUU")
WDInew <- filter(WDInew, CountryCode != "ECA")
WDInew <- filter(WDInew, CountryCode != "ECS")
WDInew <- filter(WDInew, CountryCode != "EMU")
WDInew <- filter(WDInew, CountryCode != "EAP")
WDInew <- filter(WDInew, CountryCode != "EAS")
WDInew <- filter(WDInew, CountryCode != "CEB")
WDInew <- filter(WDInew, CountryCode != "ARB")
WDInew <- filter(WDInew, CountryCode != "NAC")


WDI2 <- filter(WDInew, IndicatorCode == "AG.LND.FRST.ZS" | IndicatorCode == "EG.FEC.RNEW.ZS"|IndicatorCode == "EG.USE.COMM.FO.ZS"|IndicatorCode == "EG.ELC.ACCS.ZS"| IndicatorCode == "EN.ATM.CO2E.PC"| IndicatorCode == "EN.ATM.GHGO.KT.CE"|IndicatorCode == "EN.ATM.METH.KT.CE"|IndicatorCode == "ER.PTD.TOTL.ZS"| IndicatorCode == "EN.POP.DNST"|IndicatorCode == "ER.PTD.TOTL.ZS"|IndicatorCode == "FP.CPI.TOTL.ZG"|IndicatorCode == "GC.XPN.COMP.ZS"|IndicatorCode == "IC.FRM.CRIM.ZS"|IndicatorCode == "IC.FRM.FEMM.ZS"|IndicatorCode == "IC.LGL.CRED.XQ"|IndicatorCode == "IT.CEL.SETS.P2"|IndicatorCode == "IT.NET.USER.P2"|IndicatorCode == "MS.MIL.XPND.GD.ZS"|IndicatorCode == "NY.GDP.PCAP.CD"|IndicatorCode == "NY.GDP.MKTP.PP.CD"|IndicatorCode == "NY.GDP.PCAP.KD.ZG"|IndicatorCode == "SE.ADT.1524.LT.ZS"|IndicatorCode == "SE.ADT.LITR.ZS"|IndicatorCode == "SG.GEN.PARL.ZS"|IndicatorCode == "SG.VAW.REAS.ZS"|IndicatorCode == "SH.DTH.MORT"|IndicatorCode == "SI.POV.GINI"|IndicatorCode == "SL.EMP.WORK.ZS"|IndicatorCode == "SL.FAM.0714.ZS"|IndicatorCode == "SL.UEM.NEET.ZS"|IndicatorCode == "SM.POP.TOTL.ZS"|IndicatorCode == "SN.ITK.DFCT"|IndicatorCode == "SP.DYN.LE00.IN"|IndicatorCode == "SP.UWT.TFRT"|IndicatorCode == "ST.INT.DPRT"|IndicatorCode == "SP.POP.TOTL"|IndicatorCode == "VC.IHR.PSRC.P5")


#read.csv("F://IntroDSproject/ourWDI.csv")


#WDI2 <- filter(WDInew, IndicatorCode == "AG.LND.FRST.ZS" | IndicatorCode == "EG.FEC.RNEW.ZS"|IndicatorCode == "EG.USE.COMM.FO.ZS"|IndicatorCode == "EG.ELC.ACCS.ZS"| IndicatorCode == "EN.ATM.CO2E.PC"| IndicatorCode == "EN.ATM.GHGO.KT.CE"|IndicatorCode == "EN.ATM.METH.KT.CE"|IndicatorCode == "ER.PTD.TOTL.ZS"| IndicatorCode == "EN.POP.DNST"|IndicatorCode == "ER.PTD.TOTL.ZS"|IndicatorCode == "FP.CPI.TOTL.ZG"|IndicatorCode == "GC.XPN.COMP.ZS"|IndicatorCode == "IC.FRM.CRIM.ZS"|IndicatorCode == "IC.FRM.FEMM.ZS"|IndicatorCode == "IC.LGL.CRED.XQ"|IndicatorCode == "IT.CEL.SETS.P2"|IndicatorCode == "IT.NET.USER.P2"|IndicatorCode == "MS.MIL.XPND.GD.ZS"|IndicatorCode == "NY.GDP.PCAP.CD"|IndicatorCode == "NY.GDP.MKTP.PP.CD"|IndicatorCode == "NY.GDP.PCAP.KD.ZG"|IndicatorCode == "SE.ADT.1524.LT.ZS"|IndicatorCode == "SE.ADT.LITR.ZS"|IndicatorCode == "SG.GEN.PARL.ZS"|IndicatorCode == "SG.VAW.REAS.ZS"|IndicatorCode == "SH.DTH.MORT"|IndicatorCode == "SI.POV.GINI"|IndicatorCode == "SL.EMP.WORK.ZS"|IndicatorCode == "SL.FAM.0714.ZS"|IndicatorCode == "SL.UEM.NEET.ZS"|IndicatorCode == "SM.POP.TOTL.ZS"|IndicatorCode == "SN.ITK.DFCT"|IndicatorCode == "SP.DYN.LE00.IN"|IndicatorCode == "SP.UWT.TFRT"|IndicatorCode == "ST.INT.DPRT"|IndicatorCode == "SP.POP.TOTL"|IndicatorCode == "VC.IHR.PSRC.P5")

write.csv(WDI2, file = "ourWDI.csv")
WDI4<- select(WDI2,"CountryName","CountryCode", "IndicatorCode", "Year","Value")

comm<- WDI4 %>% filter(IndicatorCode == "IT.CEL.SETS.P2"|IndicatorCode == "IT.NET.USER.P2")  %>% spread(IndicatorCode, Value)
write.csv(comm, file = "Communication.csv")

econ<- WDI4 %>% filter(IndicatorCode == "FP.CPI.TOTL.ZG"|IndicatorCode == "IC.LGL.CRED.XQ") %>% spread(IndicatorCode, Value)
write.csv(econ, file = "Economy.csv")

edu <- WDI4 %>% filter(IndicatorCode == "SE.ADT.1524.LT.ZS" | IndicatorCode == "SE.ADT.LITR.ZS" | IndicatorCode == "SG.GEN.PARL.ZS" | IndicatorCode == "SG.VAW.REAS.ZS") %>% spread(IndicatorCode, Value)
write.csv(edu, file = "Education.csv")

emissions<- WDI4%>% filter(IndicatorCode == "EN.ATM.CO2E.PC")%>% spread(IndicatorCode, Value)
write.csv(emissions, file = "Emissions.csv")

energy<- WDI4%>% filter(IndicatorCode == "EG.FEC.RNEW.ZS"|IndicatorCode == "EG.USE.COMM.FO.ZS"|IndicatorCode == "EG.ELC.ACCS.ZS") %>% spread(IndicatorCode, Value)
write.csv(energy, file = "Energy.csv")

environnment1<- WDI4 %>% filter(IndicatorCode == "ER.PTD.TOTL.ZS"|IndicatorCode == "AG.LND.FRST.ZS") %>% spread(IndicatorCode, Value)
write.csv(environnment1, file = "Environment.csv")


GDP<- WDI4 %>% filter(IndicatorCode == "MS.MIL.XPND.GD.ZS"|IndicatorCode == "NY.GDP.PCAP.CD"|IndicatorCode == "NY.GDP.MKTP.PP.CD"|IndicatorCode == "NY.GDP.PCAP.KD.ZG") %>% spread(IndicatorCode, Value)
write.csv(GDP, file = "GDP.csv")

population<- WDI4 %>% filter(IndicatorCode == "SH.DTH.MORT"|IndicatorCode == "SI.POV.GINI"|IndicatorCode == "SL.EMP.WORK.ZS"|IndicatorCode == "SL.FAM.0714.ZS"|IndicatorCode == "SL.UEM.NEET.ZS"|IndicatorCode == "SM.POP.TOTL.ZS"|IndicatorCode == "SN.ITK.DFCT"|IndicatorCode == "SP.DYN.LE00.IN"|IndicatorCode == "SP.UWT.TFRT"|IndicatorCode == "ST.INT.DPRT"|IndicatorCode == "SP.POP.TOTL"|IndicatorCode == "VC.IHR.PSRC.P5"| IndicatorCode == "EN.POP.DNST") %>% spread(IndicatorCode, Value)

write.csv(population, file = "Population.csv")

```
(AG.LND.FRST.ZS	Forest area (% of land area), 
EG.ELC.ACCS.ZS	Access to electricity (% of population) 
EG.FEC.RNEW.ZS	Renewable energy consumption (% of total final energy consumption), 
EG.USE.COMM.FO.ZS	Fossil fuel energy consumption (% of total), 
EN.ATM.CO2E.PC	CO2 emissions (metric tons per capita), 
EN.ATM.GHGO.KT.CE	Other greenhouse gas emissions, HFC, PFC and SF6 (thousand metric tons of CO2 equivalent), 
EN.ATM.HFCG.KT.CE	HFC gas emissions (thousand metric tons of CO2 equivalent, 
EN.ATM.METH.KT.CE	Methane emissions (kt of CO2 equivalent), 
EN.FSH.THRD.NO	Fish species, threatened, 
EN.HPT.THRD.NO	Plant species (higher), threatened, 
EN.MAM.THRD.NO	Mammal species, threatened, 
EN.POP.DNST	Population density (people per sq. km of land area), 
ER.BDV.TOTL.XQ	GEF benefits index for biodiversity (0 = no biodiversity potential to 100 = maximum), 
ER.PTD.TOTL.ZS	Terrestrial and marine protected areas (% of total territorial area), 
FP.CPI.TOTL.ZG	Inflation, consumer prices (annual %), 
GC.XPN.COMP.ZS	Compensation of employees (% of expense), 
IC.FRM.CRIM.ZS	Losses due to theft, robbery, vandalism, and arson (% sales), 
IC.FRM.FEMM.ZS	Firms with female top manager (% of firms),
IC.LGL.CRED.XQ	Strength of legal rights index (0=weak to 12=strong),
IT.CEL.SETS.P2	Mobile cellular subscriptions (per 100 people), 
IT.NET.USER.P2	Internet users (per 100 people), 
MS.MIL.XPND.GD.ZS	Military expenditure (% of GDP), 
NY.GDP.PCAP.CD	GDP per capita (current USdollar), NY.GDP.MKTP.PP.CD	GDP, PPP (current international dollar), 
NY.GDP.PCAP.KD.ZG	GDP per capita growth (annual %), 
SE.ADT.1524.LT.ZS	Youth literacy rate, population 15-24 years, both sexes (%), 
SE.ADT.LITR.ZS	Adult literacy rate, population 15+ years, both sexes (%), 
SG.GEN.PARL.ZS	Proportion of seats held by women in national parliaments (%), 
SG.VAW.REAS.ZS	Women who believe a husband is justified in beating his wife (any of five reasons) (%),
SH.DTH.MORT	Number of under-five deaths), 
SI.POV.GINI	GINI index (World Bank estimate), 
SL.EMP.WORK.ZS	Wage and salaried workers, total (% of total employed), 
SL.FAM.0714.ZS	Children in employment, unpaid family workers (% of children in employment, ages 7-14),
SL.UEM.NEET.ZS	Share of youth not in education, employment, or training, total (% of youth population, SM.POP.TOTL.ZS	International migrant stock (% of population),
SN.ITK.DFCT	Depth of the food deficit (kilocalories per person per day), 
SP.DYN.LE00.IN	Life expectancy at birth, total (years), 
SP.UWT.TFRT	Unmet need for contraception (% of married women ages 15-49), 
ST.INT.DPRT	International tourism, number of departures, 
SP.POP.TOTL	Population, total, 
VC.IHR.PSRC.P5	Intentional homicides (per 100,000 people))

```{r}
ourWDI <- read_csv("d:/Documents/GitHub/IntroDSproject/ourWDI.csv")
head(ourWDI)

```


#https://www.kaggle.com/benhamner/indicators-in-data

