---
title: "WDI"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(readr)
Indicators_csv <- read_csv("d:/Documents/IntroDSproject/Indicators_csv")
library(tidyverse)

WDI <- filter(Indicators_csv, Year == "2010"| Year == "2011" | Year == "2012"| Year == "2013" | Year == "2014" | Year == "2015" | Year == "2016" | Year =="2017")


WDI2 <- filter(WDI, IndicatorCode == "AG.LND.FRST.ZS" |IndicatorCode == "EG.ELC.ACCS.ZS" | IndicatorCode == "EG.ELC.HYRO.ZS" |IndicatorCode == "EG.ELC.RNWX.KH" | IndicatorCode == "EG.FEC.RNEW.ZS"|IndicatorCode == "EG.USE.COMM.FO.ZS"|IndicatorCode == "EN.ATM.CO2E.KT"| IndicatorCode == "EN.ATM.CO2E.PC"| IndicatorCode == "EN.ATM.GHGO.KT.CE"| IndicatorCode == "EN.ATM.HFCG.KT.CE"|IndicatorCode == "EN.ATM.METH.KT.CE"| IndicatorCode == "EN.FSH.THRD.NO"|IndicatorCode == "EN.HPT.THRD.NO"|IndicatorCode == "EN.MAM.THRD.NO"| IndicatorCode == "EN.POP.DNST"|IndicatorCode == "ER.BDV.TOTL.XQ"|IndicatorCode == "ER.H2O.INTR.PC"|IndicatorCode == "ER.PTD.TOTL.ZS"|IndicatorCode == "FP.CPI.TOTL.ZG"|IndicatorCode == "GC.REV.SOCL.ZS"|IndicatorCode == "GC.XPN.COMP.ZS"|IndicatorCode == "IC.FRM.CRIM.ZS"|IndicatorCode == "IC.FRM.FEMM.ZS"|IndicatorCode == "IC.FRM.FEMO.ZS"|IndicatorCode == "IC.LGL.CRED.XQ"|IndicatorCode == "IP.JRN.ARTC.SC"|IndicatorCode == "IT.CEL.SETS"|IndicatorCode == "IT.CEL.SETS.P2"|IndicatorCode == "IT.MLT.MAIN.P2"|IndicatorCode == "IT.NET.BBND.P2"|IndicatorCode == "IT.NET.USER.P2"|IndicatorCode == "MS.MIL.XPND.GD.ZS"|IndicatorCode == "NE.DAB.TOTL.ZS"| IndicatorCode == "NY.GDP.MKTP.CD"|IndicatorCode == "NY.GDP.MKTP.KD.ZG"|IndicatorCode == "NY.GDP.PCAP.CD"|IndicatorCode == "NY.GDP.MKTP.PP.CD"|IndicatorCode == "NY.GDP.PCAP.KD.ZG"|IndicatorCode == "per_allsp.adq_pop_tot"|IndicatorCode == "per_allsp.cov_pop_tot"|IndicatorCode == "SE.ADT.1524.LT.ZS"|IndicatorCode == "SE.ADT.LITR.FE.ZS"|IndicatorCode == "SE.ADT.LITR.ZS"|IndicatorCode == "SE.PRM.CMPT.FE.ZS"|IndicatorCode == "SE.PRM.CMPT.MA.ZS"|IndicatorCode == "SG.GEN.PARL.ZS"|IndicatorCode == "SG.VAW.REAS.ZS"|IndicatorCode == "SH.DTH.MORT"|IndicatorCode == "SI.POV.GINI"|IndicatorCode == "SL.EMP.WORK.ZS"|IndicatorCode == "SL.FAM.0714.ZS"|IndicatorCode == "SL.UEM.1524.NE.ZS"|IndicatorCode == "SL.UEM.NEET.ZS"|IndicatorCode == "SM.POP.TOTL.ZS"|IndicatorCode == "SN.ITK.DFCT"|IndicatorCode == "SP.DYN.LE00.IN"|IndicatorCode == "SP.UWT.TFRT"|IndicatorCode == "ST.INT.DPRT"|IndicatorCode == "SP.POP.TOTL"|IndicatorCode == "VC.IHR.PSRC.P5")

write.csv(WDI2, file = "ourWDI.csv")



```
(AG.LND.FRST.ZS	Forest area (% of land area), 
EG.ELC.ACCS.ZS	Access to electricity (% of population) 
EG.ELC.HYRO.ZS,	Electricity production from hydroelectric sources (% of total),
EG.ELC.RNWX.KH	Electricity production from renewable sources, excluding hydroelectric (kWh), EG.FEC.RNEW.ZS	Renewable energy consumption (% of total final energy consumption), 
EG.USE.COMM.FO.ZS	Fossil fuel energy consumption (% of total), 
EN.ATM.CO2E.KT	CO2 emissions (kt), 
EN.ATM.CO2E.PC	CO2 emissions (metric tons per capita), 
EN.ATM.GHGO.KT.CE	Other greenhouse gas emissions, HFC, PFC and SF6 (thousand metric tons of CO2 equivalent), 
EN.ATM.HFCG.KT.CE	HFC gas emissions (thousand metric tons of CO2 equivalent, 
EN.ATM.METH.KT.CE	Methane emissions (kt of CO2 equivalent), 
EN.FSH.THRD.NO	Fish species, threatened, 
EN.HPT.THRD.NO	Plant species (higher), threatened, 
EN.MAM.THRD.NO	Mammal species, threatened, 
EN.POP.DNST	Population density (people per sq. km of land area), 
ER.BDV.TOTL.XQ	GEF benefits index for biodiversity (0 = no biodiversity potential to 100 = maximum), ER.H2O.INTR.PC	Renewable internal freshwater resources per capita (cubic meters),
ER.PTD.TOTL.ZS	Terrestrial and marine protected areas (% of total territorial area), 
FP.CPI.TOTL.ZG	Inflation, consumer prices (annual %), 
GC.REV.SOCL.ZS	Social contributions (% of revenue), 
GC.XPN.COMP.ZS	Compensation of employees (% of expense), 
IC.FRM.CRIM.ZS	Losses due to theft, robbery, vandalism, and arson (% sales), 
IC.FRM.FEMM.ZS	Firms with female top manager (% of firms),
IC.FRM.FEMO.ZS	Firms with female participation in ownership (% of firms), 
IC.LGL.CRED.XQ	Strength of legal rights index (0=weak to 12=strong),
IP.JRN.ARTC.SC	Scientific and technical journal articles,
IT.CEL.SETS	Mobile cellular subscriptions,
IT.CEL.SETS.P2	Mobile cellular subscriptions (per 100 people), 
IT.MLT.MAIN.P2	Fixed telephone subscriptions (per 100 people), 
IT.NET.BBND.P2	Fixed broadband subscriptions (per 100 people), 
IT.NET.USER.P2	Internet users (per 100 people), 
MS.MIL.XPND.GD.ZS	Military expenditure (% of GDP), 
NE.DAB.TOTL.ZS	Gross national expenditure (% of GDP), 
NY.GDP.MKTP.CD	GDP at market prices (current USdollar), 
NY.GDP.MKTP.KD.ZG	GDP growth (annual %), NY.GDP.PCAP.CD	GDP per capita (current USdollar), NY.GDP.MKTP.PP.CD	GDP, PPP (current international dollar), 
NY.GDP.PCAP.KD.ZG	GDP per capita growth (annual %), 
per_allsp.adq_pop_tot	Adequacy of social protection and labor programs (% of total welfare of beneficiary households),
per_allsp.cov_pop_tot	Coverage (%) -All Social Protection and Labor, 
SE.ADT.1524.LT.ZS	Youth literacy rate, population 15-24 years, both sexes (%), 
SE.ADT.LITR.FE.ZS	Adult literacy rate, population 15+ years, female (%),
SE.ADT.LITR.ZS	Adult literacy rate, population 15+ years, both sexes (%), 
SE.PRM.CMPT.FE.ZS	Primary completion rate, female (%), 
SE.PRM.CMPT.MA.ZS	Primary completion rate, male (%), 
SG.GEN.PARL.ZS	Proportion of seats held by women in national parliaments (%), 
SG.VAW.REAS.ZS	Women who believe a husband is justified in beating his wife (any of five reasons) (%),
SH.DTH.MORT	Number of under-five deaths), 
SI.POV.GINI	GINI index (World Bank estimate), 
SL.EMP.WORK.ZS	Wage and salaried workers, total (% of total employed), 
SL.FAM.0714.ZS	Children in employment, unpaid family workers (% of children in employment, ages 7-14), SL.UEM.1524.NE.ZS	Unemployment, youth total (% of total labor force ages 15-24) (national estimate),
SL.UEM.NEET.ZS	Share of youth not in education, employment, or training, total (% of youth population, SM.POP.TOTL.ZS	International migrant stock (% of population),
SN.ITK.DFCT	Depth of the food deficit (kilocalories per person per day), 
SP.DYN.LE00.IN	Life expectancy at birth, total (years), 
SP.UWT.TFRT	Unmet need for contraception (% of married women ages 15-49), 
ST.INT.DPRT	International tourism, number of departures, 
SP.POP.TOTL	Population, total, VC.IHR.PSRC.P5	Intentional homicides (per 100,000 people))

#https://www.kaggle.com/benhamner/indicators-in-data
